---
title: "Excercises week 2"
author: "Jakob"
date: "2/9/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
```

3.1 
Weighted averages: A survey is conducted in a certain city regarding support for increased
property taxes to fund schools. In this survey, higher taxes are supported by 50% of respondents
aged 18–29, 60% of respondents aged 30–44, 40% of respondents aged 45–64, and 30% of
respondents aged 65 and up. Assume there is no nonresponse.
Suppose the sample includes 200 respondents aged 18–29, 250 aged 30–44, 300 aged 45–64,
and 250 aged 65+. Use the weighted average formula to compute the proportion of respondents
in the sample who support higher taxes.

```{r}
(0.5*200+0.60*250+0.4*300+0.3*250)/1000
```
3.3 
Probability distributions: Using R, graph probability densities for the normal distribution,
plotting several different curves corresponding to different choices of mean and standard
deviation parameters.

```{r}
x = seq(from=-3,to=3, length.out=1000)
y1=dnorm(x, mean=0, sd=1)
y2=dnorm(x, mean=2, sd=0.2)
plot(x,y1)
plot(x,y2)
```

3.4
Probability distributions: Using a bar plot in R, graph the Poisson distribution with parameter

```{r}
x = 1:20
y=dpois(x, lambda = 3.5)
plot(x,y)
tibble(x=x,y=y) %>% 
  ggplot(aes(x,y)) +
  geom_col()
```
3.5 
Probability distributions: Using a bar plot in R, graph the binomial distribution with n = 20 and p= 0.3

```{r}
x = 1:20
y=dbinom(x, size = 20, prob = 0.3 )
plot(x,y)
tibble(x=x,y=y) %>% 
  ggplot(aes(x,y)) +
  geom_col()
```
3.6 
Linear transformations: A test is graded from 0 to 50, with an average score of 35 and a standard
deviation of 10. For comparison to other tests, it would be convenient to rescale to a mean of
100 and standard deviation of 15.
(a) Labeling the original test scores as x and the desired rescaled test score as y, come up with a
linear transformation, that is, values of 0 and 1 so that the rescaled scores ~ = 0   1G have a
mean of 100 and a standard deviation of 15.
(b) What is the range of possible values of this rescaled score ~?
(c) Plot the line showing ~ vs. G.

```{r}
x=rnorm(100000000, mean = 35, sd=10)
y=65+x*1.5
plot(x,y)
hist(y)
```

